Predator clusters

### 2023-03-14 reports/04_pred_clus.qmd
Repeat analysis with 3 clusters

>>>>

## 3-cluster analysis

```{r}
#| label: predator_dendro2

# Cut predators into 3 clusters
clust <- cutree(sightings_clust, 3)
g <- split(names(clust), clust)
p <- ggtree(sightings_clust, hang = -1)
pred_clust_mrca <- sapply(g, function(n) MRCA(p, n))

```{r}
#| label: predator_mosaic2
#| warning: false

```{r}
#| label: indicator_species2

species_wide <- pivot_wider(predators_abundant,
                            names_from = species,
                            values_from = count,
                            values_fill = 0) %>% 
  column_to_rownames("amlr.station")
cluster_indval <- labdsv::indval(species_wide, clust)
indval_mtx <- cluster_indval$indval
indval_fmt <- apply(indval_mtx, 2, function(x) {
  ord <- order(x, decreasing = TRUE)
  result <- ifelse(x >= 0.25, 
         str_glue("{rownames(indval_mtx)} ({round(x * 100)}%)"),
         NA) %>% 
    `[`(ord) %>% 
    na.omit() %>% 
    paste(collapse = "<br>")
  ifelse(result == "", "None", result)
})
as_tibble(t(indval_fmt)) %>% 
  knitr::kable(format = "html", escape = FALSE) %>% 
  kableExtra::kable_styling()
```

```{r}
#| label: cluster_maps2
